First Exclusive Measurement of Deep Virtual Compton Scattering off $^4$He: Toward the 3D tomography of nuclei

### 2017-01-27 eg6-letters/DVCS-coh-He4/dvcs_he4_prl.tex
minor fixing
formating the references
Edit first 3 paragraphs

%
\date{\today}
%
\begin{abstract}
We report the first exclusive measurements of deeply virtual Compton scattering 
(DVCS) off a nucleus, where all the products of the reaction including the 
recoil $^4$He nucleus were detected. The experiment was performed using the 
Jefferson Lab CEBAF Large Acceptance Spectrometer (CLAS) enhanced with a radial 
time projection chamber (RTPC) to detect the recoiling $^4$He nuclei. We 
measure large beam spin asymmetries comparable to the proton's ones and extract 
in a model independent way, the single chirally-even generalized parton 
distribution of the $^4$He nucleus. These are pioneering measurements and will 
lead the way toward the 3D imaging of the partonic structure of nuclei.  
\end{abstract}
\pacs{Valid PACS appear here}

@@

A wealth of information on the quantum chromodynamics (QCD) structure of 
hadrons lies in the correlations between the momentum and spatial degrees of 
freedom of the fundamental constituent partons, quarks and gluons. Such 
correlations are accessible via the generalized parton distributions (GPDs).  
The GPDs correspond to the coherence between quantum states of different (or 
same) helicity, longitudinal momentum, and transverse position. In an impact 
parameter space, they can be interpreted as a distribution in the transverse 
plane of partons carrying a certain longitudinal momentum 
\cite{Burkardt:2000za,Diehl:2002he,Belitsky:2002ep}. A crucial feature of GPDs 
is the access to the transverse position of partons which, combined with their 
longitudinal momentum, leads to the total angular momentum of partons 
\cite{Burkardt:2005hp}. Deep virtual Compton scattering (DVCS) corresponding to 
hard exclusive electroproduction of a real photon, which is considered as the 
cleanest probe to access GPDs and thus study the 3D imaging of nucleons and 
nuclei.

DVCS measurements have been the focus of a worldwide effort 
\cite{Stepanyan:2001sm,Airapetian,Chekanov:2003ya,Aktas:2005ty,Chen:2006na,Munoz 
Camacho:2006hx,Girod:2007aa,Gavalian:2009,Seder:2015,Pisano:2015,Jo:2015ema} 
involving several accelerator facilities such as Jefferson Lab (JLab), HERA and  
CERN. The vast majority of the experiments focused on the study of the 
nucleon's structure. The deuterium was also investigated at HERMES and JLab 
\cite{Mazouz:2007aa} mainly as a neutron target. However, studying the 3D 
imaging of the nucleon is a very important goal, understanding how these 
distributions are modified to provide the binding and structure in a nucleus is 
as fascinating of a question and an integral part of our quest of using QCD to 
explore nuclear matter.

A DVCS process on a nuclear target differ from single nucleon scattering in 
providing access to the measure two DVCS channels. In the coherent DVCS 
channel, the target nucleus ($A$) remains intact and recoils as a whole while 
emitting a real photon ($eA \rightarrow e' A' \gamma$), allowing to measure the 
nuclear GPDs of the target. In the incoherent channel, the nucleus breaks up 
and the DVCS takes place on a bound nucleon ($N$) that emits the final photon 
($eA \rightarrow e' N' \gamma$ X), enabling the GPDs measurement of the bound 
nucleons and to study their modifications in the nuclear medium via the GPDs.  
Figure \ref{fig:diags} illustrates the dominant mechanism for the coherent DVCS 
channel on $^4$He. At sufficiently large squared electron momentum transfer 
$Q^2$ ($= -(k-k')^{2}$) and small squared momentum transfer $t$ ($= 
(p-p')^{2}$), the QCD factorization theorem predicts that the DVCS handbag 
diagram can be factorized into two parts, hard and soft parts 
\cite{Freund_Collins,Ji_Osborne}. The hard part includes photons-quark 
interaction and it is calculable through perturbative methods, while the 
soft/non-perturbative part is parametrized in terms of GPDs, which embed the 
partonic structure of the hadron.  
\begin{figure}[tb]
\includegraphics[width=6.5cm]{figs/DVCS_diagram.pdf}
\caption{Representation of the leading-order, twist-2, handbag diagram of the 
DVCS process off $^4$He.}
\label{fig:diags}
\end{figure}

%introduction
The GPDs are defined for each quark flavor and gluon as matrix
elements of the light cone operators \cite{Belitsky}, describing the transition 
between the initial and final states of a hadron. The GPDs depend on two 
longitudinal momentum fraction variables ($x$, $\xi$) and on the momentum 
transfer $t$ to the target. $x$ is the average longitudinal momentum fraction 
of the parton involved in the process and $\xi$ is the longitudinal fraction of 
the momentum transfer $t$, which is related to the Bjorken variable $x_{B}$: 
$\xi\approx {{x_B}\over{2-x_B}}$, where $x_B=\frac{Q^2}{2M\nu}$ with
the proton mass $M$ and $\nu=E_e-E_{e^\prime}$. The GPDs $x$ variable cannot be 
measured experimentally in a DVCS reaction. Hence, we measure the their 
convolutions on $x$, the so-called Compton Form Factors (CFF) 
\cite{Guidal:2013rya}.  In a DVCS process, the number of GPDs needed to 
parametrize the partonic structure of a hadron depends on the different 
configurations between the spin of the hadron and the helicity direction of the 
struck quark.  Therefore, the partonic structure of spin zero nuclei, such as 
$^4He$ and $^{12}C$, is parametrized by only one GPD ($H_{A}(x,\xi,t)$) at 
leading twist, while 4 GPDs arise in the nucleon case.  In this work, we have 
chose the $^4$He nucleus as our target of interest because of it's spinless 
nature and it shows a clear EMC effect \cite{JSeely}, in addition of having a 
high density and it is a well-known few-body system.

>>>>

%
\date{\today}
%
\begin{abstract}
We report the first fully exclusive measurement of deeply virtual Compton 
scattering (DVCS) off a nucleus for $A>1$. The experiment used the 6 GeV 
electron beam from Jefferson Lab projected onto a $^4$He target in the center of the CEBAF 
Large Acceptance Spectrometer (CLAS). An additional radial time projection 
chamber (RTPC) was used to detect the recoiling $^4$He nuclei and ensure the 
exclusivity of the process. We measured beam spin asymmetries significantly
larger than the one observed on proton targets and extract,
in a completely model independent way, the chiral even generalized parton 
distribution (GPD) of the $^4$He nucleus. This pioneering measurement 
leads the way toward the 3D imaging of the partonic structure of nuclei.
\end{abstract}
\pacs{Valid PACS appear here}

@@

A wealth of information on the quantum chromodynamics (QCD) lies in the 
internal structure of hadrons. In the recent past, the development of the 
generalized parton distributions (GPDs) framework has offered the possibility
to obtain new information about the momentum and spatial degrees of 
freedom of the quark and gluons inside hadrons [Add ref Mueller, Ji, Rad.]. 
In impact parameter space, the GPDs are indeed interpreted as a tomography of the 
transverse plane for partons carrying a certain longitudinal momentum 
\cite{Burkardt:2000za,Diehl:2002he,Belitsky:2002ep}.

The main access to GPDs is through the measurement of deep virtual Compton 
scattering (DVCS), i.e. the hard exclusive electroproduction of a real photon. 
While other processes are known to be sensitive to GPDs, the measurement of the
DVCS is considered as the cleanest probe and has been the focus of a worldwide effort 
\cite{Stepanyan:2001sm,Airapetian,Chekanov:2003ya,Aktas:2005ty,Chen:2006na,Munoz 
Camacho:2006hx,Girod:2007aa,Gavalian:2009,Seder:2015,Pisano:2015,Jo:2015ema} 
[Should we cite less publications on the topic or a review?]
involving several accelerator facilities such as Jefferson Lab (JLab), HERA and  
CERN. The vast majority of these measurements was focused on the study of the 
proton structure and allow the extraction of the tomography of the nucleon [refs].

This framework is also applicable to nuclei, giving access to completely new 
information about the nuclear structure in terms of quarks and gluons[refs to add].
The study of the 3D structure of the nuclei appears to be especially important
in light of the large nuclear effects observed in nuclear parton distribution 
functions [ref to EMC reviews]. Experimentally, the coherent DVCS channel is 
difficult to measure because of its small cross section and the necessity to
ensure that the target remains intact while emitting a hard photon 
($eA \rightarrow e' A' \gamma$). Figure \ref{fig:diags} illustrates the 
hand bag diagram for the coherent DVCS on $^4$He.

\begin{figure}[tb]
\includegraphics[width=6.5cm]{figs/DVCS_diagram.pdf}
\caption{Representation of the leading-order, twist-2, handbag diagram of the 
DVCS process off $^4$He.}
\label{fig:diags}
\end{figure}

Similarly to the proton case, at large photon's 4-momentum square  
$Q^2$ ($= -(k-k')^{2}$) and small squared momentum transfer $t$ ($= 
(p-p')^{2}$), the DVCS handbag diagram can be factorized into two parts 
\cite{Freund_Collins,Ji_Osborne}. The hard part includes photons-quark 
interaction and is calculable with perturbative QED, while the 
soft/non-perturbative part is parametrized in terms of GPDs, which embed the 
partonic structure of the hadron.

The GPDs are defined for each quark flavor and gluon as matrix
elements of the light cone operators \cite{Belitsky}, describing the transition 
between the initial and final states of a hadron. The GPDs depend on two 
longitudinal momentum fraction variables ($x$, $\xi$) and on the momentum 
transfer $t$ to the target. $x$ is the average longitudinal momentum fraction 
of the parton involved in the process and $\xi$ is the longitudinal fraction of 
the momentum transfer $t$, which is related to the Bjorken variable $x_{B}$: 
$\xi\approx {{x_B}\over{2-x_B}}$, where $x_B=\frac{Q^2}{2M\nu}$ with
the proton mass $M$ and $\nu=E_e-E_{e^\prime}$. The GPDs $x$ variable cannot be 
measured experimentally in a DVCS reaction. Hence, we measure the their 
convolutions on $x$, the so-called Compton Form Factors (CFF) 
\cite{Guidal:2013rya}.  In a DVCS process, the number of GPDs needed to 
parametrize the partonic structure of a hadron depends on the different 
configurations between the spin of the hadron and the helicity direction of the 
struck quark.  Therefore, the partonic structure of spin zero nuclei, such as 
$^4He$ and $^{12}C$, is parametrized by only one GPD ($H_{A}(x,\xi,t)$) at 
leading twist, while 4 GPDs arise in the nucleon case.  In this work, we have 
chose the $^4$He nucleus as our target of interest because of it's spinless 
nature and it shows a clear EMC effect \cite{JSeely}, in addition of having a 
high density and it is a well-known few-body system.
